%% ----------------------------------------------------------------
%% Thesis.tex -- MAIN FILE (the one that you compile with LaTeX)
%% ---------------------------------------------------------------- 

% Set up the document
\documentclass[a4paper, 11pt, oneside]{Thesis}  % Use the "Thesis" style, based on the ECS Thesis style by Steve Gunn

% Include any extra LaTeX packages required
\usepackage[square, numbers, comma, sort&compress]{natbib}  % Use the "Natbib" style for the references in the Bibliography
\usepackage[nottoc]{tocbibind} % bind bibliography to the table of contents
\usepackage{verbatim}  % Needed for the "comment" environment to make LaTeX comments
\usepackage{vector}  % Allows "\bvec{}" and "\buvec{}" for "blackboard" style bold vectors in maths
\usepackage[table]{xcolor}
\hypersetup{urlcolor=black, colorlinks=true}  % Colours hyperlinks in black, can be distracting if there are many links and colored blue.
\usepackage{graphicx}
\graphicspath{{Figures/}}  % Location of the graphics files (set up for graphics to be in PDF format)

%% ----------------------------------------------------------------
\begin{document}
\frontmatter      % Begin Roman style (i, ii, iii, iv...) page numbering

% Set up the Title Page
\title  {DynamiCrypt}
\authors  {Artiom Sumigora}
            
\addresses  {\groupname\\\deptname\\\univname}  % Do not change this here, instead these must be set in the "Thesis.cls" file, please look through it instead
\date       {\today}
\subject    {}
\keywords   {}

\maketitle
%% ----------------------------------------------------------------

\setstretch{1.3}  % It is better to have smaller font and larger line spacing than the other way round

% Define the page headers using the FancyHdr package and set up for one-sided printing
\fancyhead{}  % Clears all page headers and footers
\rhead{\thepage}  % Sets the right side header to show the page number
\lhead{}  % Clears the left side page header

\pagestyle{fancy}  % Finally, use the "fancy" page style to implement the FancyHdr headers

%% ----------------------------------------------------------------
% Declaration Page required for the Thesis
\Declaration{

\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics

I, Artiom Sumigora, declare that this thesis titled, `DynamiCrypt' and the work presented in it are my own. I confirm that:

\begin{itemize} 
\item[\tiny{$\blacksquare$}] This work was done wholly or mainly while in candidature for an undergraduate degree at Cork Institute of Technology.
 
\item[\tiny{$\blacksquare$}] Where any part of this thesis has previously been submitted for a degree or any other qualification at Cork Institute of Technology or any other institution, this has been clearly stated.
 
\item[\tiny{$\blacksquare$}] Where I have consulted the published work of others, this is always clearly attributed.
 
\item[\tiny{$\blacksquare$}] Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this project report is entirely my own work.
 
\item[\tiny{$\blacksquare$}] I have acknowledged all main sources of help.
 
\item[\tiny{$\blacksquare$}] Where the thesis is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.
\\
\end{itemize}
 
 
Signed:\\
\rule[1em]{25em}{0.5pt}  % This prints a line for the signature
 
Date:\\
\rule[1em]{25em}{0.5pt}  % This prints a line to write the date
}
\clearpage  % Declaration ended, now start a new page

%% ----------------------------------------------------------------

% The Abstract Page
\addtotoc{Abstract}  % Add the "Abstract" page entry to the Contents
\abstract{
\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics

In today's world information is mostly sent in an encrypted form over the public internet. Traditionally when a client connects to a server the public keys are shared and the same set of public/private key pairs are used for the session and potentially for future sessions, depending on how the system is setup. Provided that industry standard encryption is used it would take the attacker longer than the lifetime of the earth to crack the key making the system secure. The problem arises if the attacker managed to get the key in some other fashion other than brute force and got access to the server it would be possible to locate this key and use it to decrypt potentially sensitive information that was captured over the network.

The problem this project proposes to address is that scenario. This will be addressed by using multiple encryption keys throughout the session. These encryption keys will be generated using a tree parity machine. A tree parity machine consists of input neurons, hidden neurons and one output neuron. A neural network is chosen for this because the weights of neural networks can be synchronised between each tree parity machine on different hosts. The weights can then be used to generate a key and since the weights on both tree parity machines are identical the same key will be generated. The weight are synchronised over the network with no information sent about the weights itself therefore the attacker will not be able to figure out the key. The server can then use multiple tree parity machines to synchronise with the same number of tree parity machines on a different server and thus multiple keys will be generated and different keys can be used through a session.

This thesis will provide a program that is capable of handling synchronisation between multiple tree parity machines between two hosts. An API will be provided that will access the said program and allow other server to use dynamic encryption. A NodeJS module will also be provided to make integration with NodeJS applications very easy.

}

\clearpage  % Abstract ended, start a new page
%% ----------------------------------------------------------------

\setstretch{1.3}  % Reset the line-spacing to 1.3 for body text (if it has changed)

% The Acknowledgements page, for thanking everyone
\acknowledgements{
\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics
This project has taken a substantial amount of work, dedication and research. I would
like to say special thanks to:

Dr. John Creagh, project supervisor in semester one.

}
\clearpage  % End of the Acknowledgements
%% ----------------------------------------------------------------

\pagestyle{fancy}  %The page style headers have been "empty" all this time, now use the "fancy" headers as defined before to bring them back


%% ----------------------------------------------------------------
\lhead{\emph{Contents}}  % Set the left side page header to "Contents"
\tableofcontents  % Write out the Table of Contents

%% ----------------------------------------------------------------
\lhead{\emph{List of Figures}}  % Set the left side page header to "List if Figures"
\listoffigures  % Write out the List of Figures

%% ----------------------------------------------------------------
\lhead{\emph{List of Tables}}  % Set the left side page header to "List of Tables"
\listoftables  % Write out the List of Tables

%% ----------------------------------------------------------------
\setstretch{1.5}  % Set the line spacing to 1.5, this makes the following tables easier to read
\clearpage  % Start a new page
\lhead{\emph{Abbreviations}}  % Set the left side page header to "Abbreviations"
\listofsymbols{ll}  % Include a list of Abbreviations (a table of two columns)
{
% \textbf{Acronym} & \textbf{W}hat (it) \textbf{S}tands \textbf{F}or \\
\textbf{TPM} & \textbf{T}ree \textbf{P}arity \textbf{M}achine \\
\textbf{API} & \textbf{A}pplication \textbf{P}rotocol \textbf{I}nterface \\
\textbf{HTTP} & \textbf{H}yper \textbf{T}ext \textbf{T}ransfer \textbf{P}rotocol \\
\textbf{HTTPS} & \textbf{H}yper \textbf{T}ext \textbf{T}ransfer \textbf{P}rotocol \textbf{S}ecure \\
\textbf{SSL} & \textbf{S}ecure \textbf{S}ockets \textbf{L}ayer \\
\textbf{TLS} & \textbf{T}ransfer \textbf{L}ayer \textbf{S}ecurity \\
\textbf{AES} & \textbf{A}dvanced \textbf{E}ncryption \textbf{S}tandard \\
\textbf{RSA} & \textbf{R}ivest \textbf{S}hamir \textbf{A}dleman \\
\textbf{SSH} & \textbf{S}ecure \textbf{S}\textbf{H}ell \\
\textbf{GPG} & \textbf{G}NU \textbf{P}rivacy \textbf{G}uard \\
\textbf{GNU} & \textbf{G}\textbf{N}\textbf{U}'s Not Unix \\
\textbf{AI} & \textbf{A}rtificial \textbf{I}ntelligence \\
\textbf{GAN} & \textbf{G}enerative \textbf{A}dversarial \textbf{N}etwork \\
\textbf{IP} & \textbf{I}nternet \textbf{P}rotocol \\
\textbf{IBM} & \textbf{I}nternational \textbf{B}usiness \textbf{M}achines \\
\textbf{ID} & \textbf{I}\textbf{D}entification \\
\textbf{PHP} & \textbf{H}ypertext \textbf{P}re\textbf{P}rocessor \\
\textbf{KiB} & \textbf{K}\textbf{i}bi\textbf{B}yte \\
\textbf{TCP} & \textbf{T}ransmission \textbf{C}ontrol \textbf{P}rotocol \\
}

%% ----------------------------------------------------------------
% End of the pre-able, contents and lists of things
% Begin the Dedication page

\setstretch{1.3}  % Return the line spacing back to 1.3

\pagestyle{empty}  % Page style needs to be empty for this page
\dedicatory{Dedicated to my family\ldots}

\addtocontents{toc}{\vspace{2em}}  % Add a gap in the Contents, for aesthetics

%% ----------------------------------------------------------------
\mainmatter	  % Begin normal, numeric (1,2,3...) page numbering
\pagestyle{fancy}  % Return the page headers back to the "fancy" style

\input{Chapters/Chapter1} % Introduction

\input{Chapters/Chapter2} % Background Theory 

\input{Chapters/Chapter3} % Problem

\input{Chapters/Chapter4} % Solution Approach

\input{Chapters/Chapter5} % Conclusions and Term 2 work

%% ----------------------------------------------------------------
\label{Bibliography}
\bibliographystyle{IEEEtranN}  % Use the "IEEE Transaction" BibTeX style for formatting the Bibliography
\bibliography{Bibliography}  % The references (bibliography) information are stored in the file named "Bibliography.bib"
\lhead{\emph{Bibliography}}  % Change the left side page header to "Bibliography"

%% ----------------------------------------------------------------
% Now begin the Appendices, including them as separate files

\addtocontents{toc}{\vspace{2em}} % Add a gap in the Contents, for aesthetics

\appendix % Cue to tell LaTeX that the following 'chapters' are Appendices

\input{Appendices/AppendixA}	% Appendix Title

\input{Appendices/AppendixB} % Appendix Title

%\input{Appendices/AppendixC} % Appendix Title

\addtocontents{toc}{\vspace{2em}}  % Add a gap in the Contents, for aesthetics
\backmatter
\end{document}  % The End
%% ----------------------------------------------------------------